---
title: "Homework 1"
subtitle: "Research in Health Economics, Spring 2025"
author: "Lisbeth Vargas"
format:
    pdf: 
        output-file: "vargas-hwk1-2"
        output-ext: "pdf"
        header-includes: 
            - \usepackage{float}
            - \floatplacement{table}{H}

---

```{r}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
               
```

```{r}
#| include: false
#| eval: true

load("/Users/lisbethvargas/Desktop/GitHub/ECON 470/Homework 1/1-2/hwk1_workspace.Rdata")
```
\newpage
# Building the Data
Answer the following based on our initial, simplified dataset of enrollments, plan types, and service areas:

\noindent 1. Provide a table of the count of plans under each plan type in each year.<br>

```{r} 
#| echo: false
#| label: tbl-plans
#| tbl-cap: All plan types in 2015

options(knitr.kable.NA = 0)
knitr::kable(plan.type.year1, 
             col.names=c("Plan Type","Count"),
             format.args=list(big.mark=","), booktabs = TRUE)
```

\newpage
\noindent 2. Remove all special needs plans (SNP), employer group plans (eghp), and all "800-series" plans. Provide an updated table after making these exclusions.

```{r}
#| echo: false
#| label: tbl-plans2
#| tbl-cap: Revised plan types in 2015

options(knitr.kable.NA = 0)
knitr::kable(plan.type.year2, 
             col.names=c("Plan Type","Count"),
             format.args=list(big.mark=","), booktabs = TRUE)
``` 

\newpage
\noindent 3. Provide a table of the average enrollments for each plan type in 2015.

```{r}
#| echo: false
#| label: tbl-enroll
#| tbl-cap: Enrollments by plan type in 2015

options(knitr.kable.NA = 0)
knitr::kable(plan.type.enroll, digits=0,
             col.names=c("Plan Type","Count","Avg Enrollments"),
             format.args=list(big.mark=","), booktabs = TRUE)
``` 